\chapter{Abstract}

This project presents the development of a mobile application for managing shopping lists enhanced with price comparison and alert functionalities, supported by a service-oriented backend architecture. The solution is designed to be used in real-world contexts, such as supermarkets, allowing users to efficiently create and manage shopping lists, mark items during purchases, and access updated product prices across different stores and locations.

The system integrates multiple technologies, including a React Native mobile application, a React-based web application for shopping preparation and analysis, and a set of RESTful backend services developed in .NET. Authentication and authorization are handled by Keycloak, while push notifications are delivered through Firebase Cloud Messaging to inform users about price drops.

A central data management component is responsible for handling products, prices, and store information, ensuring consistency and reliability. The architecture follows a modular, service-oriented approach, enabling the integration of additional services and supporting data synchronization requirements.

Additionally, the project explores the concept of White Label development, allowing the customization of applications through dedicated CI/CD pipelines. The use of AI-powered tools, such as GitHub Copilot, is also incorporated to support development and validation processes.

Overall, this work demonstrates how a seemingly simple application can evolve into an advanced functional prototype with an extensible foundation for future features, addressing challenges related to distributed systems, data management, and real-time user interaction.